\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-23 paper.tex
added missing memory reduction (conclusion) + typo

Initial experiments confirm the theoretical positive impact on resource usage:
grouping of messages lowers the number of packets by 13\%, while the total
number of bytes sent over the network is reduced by 7\%. Finally, the execution
time is also improved by 7\%.

@@

Future research will focus on the integration of applications with a generated
IDS. We see opportunities for applications who detect intrusion, to actively
and dynamically respond and avoid malicious payloads.

>>>>

Initial experiments confirm the theoretical positive impact on resource usage:
grouping of messages lowers the number of packets by 13\%, while the total
number of bytes sent over the network is reduced by 7\%. The execution time is
improved by 7\% and memory usage can be reduced by even 20\%.

@@

Future research will focus on the integration of applications with a generated
IDS. We see opportunities for applications who detect intrusions, to actively
and dynamically respond and avoid malicious payloads.
